\documentclass[letterpaper,12pt]{report} 

\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsfonts,amsmath,color,amssymb,float, amsthm}  
\usepackage{hyperref}
\usepackage[right=3cm,left=2cm,top=2cm,bottom=2cm,headsep=0.7cm,footskip=0.5cm]{geometry}
\usepackage{enumerate}
\usepackage{wrapfig} 
\usepackage[rflt]{floatflt}
\usepackage{xcolor} 
\usepackage{esint}
\usepackage{cancel}
\usepackage{listings}
\usepackage{pstricks, caption}
\providecommand{\norm}[1]{\lVert#1\rVert}
\providecommand{\Arg}[1]{Arg(#1)}

\decimalpoint

\newtheorem{teorema}{Teorema}[chapter] 
\newtheorem{ejemplo}{Ejemplo}[chapter] 
\newtheorem{defi}{Definici\'on}[chapter] 
\newtheorem{corolario}{Corolario}[chapter] 
\newtheorem{propo}{Proposición}[chapter] 
\newtheorem{lema}{Lema}[chapter] 
\newcommand{\grad}{^{\circ}}

\newlength{\drop}

%%%%%%%%%%%%Fancy Chapters%%%%%%%%%%%%%%%%%
%Options: Sonny, Lenny, Glenn, Conny, Rejne, Bjarne, Bjornstrup
\usepackage[Lenny]{fncychap}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{titlepage}
 \drop=0.1\textheight
    \centering
    \vspace*{\baselineskip}
    \rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt}
    \rule{\textwidth}{0.4pt}\\[\baselineskip]
    {\scshape\Huge Cálculo IV} \\[0.2\baselineskip]
    \rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt}
    \rule{\textwidth}{1.6pt}\\[\baselineskip]
    {\Large Autor: \par}
{\Large Alejandro Saavedra \par}
\vfill
{\large Agosto 2022 \par}
{\large v1.0 \par}
\end{titlepage}
\tableofcontents

\input{./Cap-Numeros-Complejos.tex}
\input{./Cap-Funciones-Analiticas.tex}
\input{./Cap-Funciones-Elementales.tex}
\input{./Cap-Integral.tex}
\input{./Cap-Series.tex}
\input{./Cap-Residuos.tex}
\input{./Cap-Mapeos-Conformes.tex}

\begin{thebibliography}{99}

\bibitem{Agarwal} Agarwal, R. P., Perera, K. y Pinelas, S. (2011). \textit{An Introduction to Complex Analysis}. Springer New York. 

\bibitem{Aguayo} Aguayo, J. (2020). \textit{Apuntes del curso Cálculo IV}. Universidad de Concepción.

\bibitem{Apostol} Apostol, T. M. (1999). \textit{Calculus volumen I} (2da edición). Barcelona, España: Editorial Reverté, S. A.

\bibitem{Asmar} Asmar, N. H y Grafakos, L. (2018). \textit{Complex Analysis with Applications}. Springer Cham. 

\bibitem{Churchill} Churchill, R. V. y Brown J. W. (1992). \textit{Variable compleja y aplicaciones} (5ta edición). Madrid, España: McGraw-Hill.

\bibitem{Marsden} Marsden, J.E. y Hoffman, M.J. (1996). \textit{Análisis básico de variable compleja}. México: Editorial Trillas. 

\end{thebibliography}

\end{document}